Put Title here

### 2018-11-27 General WLD combinatorics.tex
finished first draft of cyclic intervals, changed lemma 3.4 accordingly and added def of weakly admissible.

\begin{dfn}\label{admisdfn}
A Wilson loop diagram is admissible if \begin{enumerate}
\item $|V| \geq |\cP| + 4$
\item There does not exists a set of propagators, $P \subset \cP$ such that $|V(P)| < |P| + 3$.
\item There does not exist a pair of propagators, $p, q \subset \cP$ such that $i_p < i_q < j_p <j_q$.
\end{enumerate}
 \end{dfn}

@@

\begin{lem}\label{lem sian 1}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
        \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
      \end{enumerate}
  \end{enumerate}
\end{lem}

\begin{proof}
  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+3)$.  By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.

@@

  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
  or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
\end{itemize}
Since $W$ contains finitely many vertices, this must eventually terminate in one of the three desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+2)$ for its support.  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $j_1)$ or $j_1+2$.  Flipping the diagram if necessary, assume the former.  Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

@@

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none.  Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise.

Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ and such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.

There are two cases to consider.
The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$.  Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.  The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.  Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.  Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $q_r$ contains only $p_{r+1}$; if $q_r$ is of length $4$ then we have \ref{item 4 and 2} and if $q_r$ is of length $5$ or $6$ then we have either \ref{item lonely 2} or an unsupported vertex, all of which are impossible.  Therefore the first case cannot occur.

@@

\begin{figure}
\includegraphics[scale=0.8]{Vdiagram}
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
\label{fig V diagram}
\end{figure}

@@

    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
    \begin{itemize}
      \item 
    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
    \[
    J^{(W)}_p(m) = [m+4, m], \quad J^{(W)}_p(m+1) = \{m+1\}, \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item
        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
    \[
    J^{(W)}_p(m) = [m+4, d-1], \quad J^{(W)}_p(m+1) = [d, m+1], \quad J^{(W)}_p(m+2) = \{m+2\}, \quad J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
    \[
    J^{(W)}_p(m) = \{m+3\}, \quad J^{(W)}_p(m+1) = [m+4, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+2\},
    \]
    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
    \[
    J^{(W)}_p(m) = [m+4, j+1], \quad J^{(W)}_p(m+1) = [j+2, d-1], \quad J^{(W)}_p(m+2) = [d, m+1], \quad J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are again as required.
    \end{itemize}

@@

\begin{align*}
  I_{j+1}^{(W)}(r) &= \begin{cases}
    j+1 & \text{if } r=q\\
    j+2 & \text{if } r=p\\
    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_m^{(W)}(r) &= \begin{cases}
    m & \text{if $r=p$ and $q$ not supported on $m$}\\
    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
    I_{m}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+1}^{(W)}(r) & = \begin{cases}
    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_{m+2}^{(W)}(r) & = \begin{cases}
    m+2 & \text{if } r=p \\
    I_{m+3}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+3}^{(W)}(r) & = \begin{cases}
    m+3 & \text{if } r=p \\
    I_{m+4}^{(V)}(r) & \text{if } r\neq p
  \end{cases}
\end{align*}
Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$. Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.  Assembling the intervals for $p$ we get, and
***I still have to fix these intervals***
\[J_p^{(W)}(c) = [c+4,e-1], \quad J_p^{(W)}(c+1) = [e,c], \quad J_p^{(W)}(c+2) = \{c+1,c+2\}, \quad J_p^{(W)}(c+3) = \{c+3\}.\]

The result now follows by induction.

>>>>

\begin{dfn}\label{admisdfn}
A Wilson loop diagram is admissible if \begin{enumerate}
\item $|V| \geq |\cP| + 4$
\item There does not exists a set of propagators, $P \subset \cP$ such that $|V(P)| < |P| + 3$.
\item There does not exist a pair of propagators, $p, q \subset \cP$ such that $i_p < i_q < j_p <j_q$.
\end{enumerate}
A Wilson loop diagram is weakly admissible if the second and third conditions hold.
 \end{dfn}

@@

\begin{lem}\label{lem sian 1}
  Let $W$ be a weakly admissible WLD with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length $\leq 6$ with a propagator of length 2 inside it and nothing else inside it.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
  %Then exactly one of the following two things occurs.
  %\begin{enumerate}
  %  \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
  %  \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
  %    \begin{enumerate}
  %      \item There is a propagator of length $2$, say $(i, i+2)$ such that no other propagators ends on either the edge $i$ or the edge $i+2$.\label{item lonely 2}
  %      \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator ends between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  %      \item There exists a propagator of length 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
  %    \end{enumerate}
  %\end{enumerate}
\end{lem}

\begin{proof}
  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+3)$.  By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.  This gives us an instance of configuration~\ref{item big and 2} from the statement.

@@

  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item big and 2} or \ref{item pair of 2s} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
  or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
\end{itemize}
Since $W$ contains finitely many vertices, this must eventually terminate in one of the desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+2)$ for its support.  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise: 
Since $p_1$ is not in configuration \ref{item pair of 2s}, there are no propagators of length $3$, and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $j_1$ or on edge $j_1-1$ or on edge $j_1-2$.  This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

@@

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none.  Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item big and 2} or \ref{item pair of 2s}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise.

Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$; such a new $q_r$ still satisfies all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.

There are two cases to consider.
The first case is that $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$.  Then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.  The only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.  Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.  Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $q_r$ contains only $p_{r+1}$ and so we have \ref{item big and 2} which again we have assumed does not occur.
Therefore the first case cannot occur.

@@

\begin{figure}
\includegraphics[scale=0.8]{Vdiagram_modified}
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 unsupported vertices labelled $l, l+1, \ldots$.}
\label{fig V diagram}
\end{figure}

@@

    Taking all the possibilities for the left two cases of Figure~\ref{fig 3 cases}, the intervals $J^{(W)}_r(*)$ are still cyclic for all $r \neq p$, and we can assemble the intervals for the $J_p^{(W)}(*)$ as follows.
    \begin{itemize}
      \item 
    If $m=l$ then either $a=2$ (so $l+1=m+1$, $j=m+2$, and $j+1=m+3$) or $a=3$ (so $l+1=m+1$, $l+2=m+2$, $j=m+3$, and $j+1$ is not in the support of $p$), and in both cases
    \[
    J^{(W)}_p(m) = [m+4, m], \  J^{(W)}_p(m+1) = \{m+1\}, \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item
        If $m=i+1$ then checking each of the three different possibilities for $a$ we likewise get
    \[
    J^{(W)}_p(m) = [m+4, d-1], \  J^{(W)}_p(m+1) = [d, m+1], \  J^{(W)}_p(m+2) = \{m+2\}, \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are nonempty and otherwise as required.
  \item If $m=i$ then $a=1$ or $a=2$, in the former case $l=m+2$, $j=m+3$ and $j+1$ is not in the support of $p$ so
    \[
    J^{(W)}_p(m) = \{m+3\}, \  J^{(W)}_p(m+1) = [m+4, d-1], \  J^{(W)}_p(m+2) = [d, m+1], \  J^{(W)}_p(m+3) = \{m+2\},
    \]
    while in the latter $l=m+2$, $l+1=m+3$, and $j$ and $j+1$ are not in the support of $p$ so
    \[
    J^{(W)}_p(m) = [m+4, j+1], \  J^{(W)}_p(m+1) = [j+2, d-1], \  J^{(W)}_p(m+2) = [d, m+1], \  J^{(W)}_p(m+3) = \{m+3\},
    \]
    which are again as required.
    \end{itemize}

@@

\begin{align*}
  I_{j+1}^{(W)}(r) &= \begin{cases}
    j+1 & \text{if } r=q\\
    j+2 & \text{if } r=p\\
    I_{j+3}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_m^{(W)}(r) &= \begin{cases}
    m & \text{if $r=p$ and $q$ not supported on $m$}\\
    m+1 & \text{if $r=p$ and $q$ supported on $m$}\\
    I_{m}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+1}^{(W)}(r) & = \begin{cases}
    m+1 & \text{if $r=p$ and $q$ not supported on $m+1$} \\
    m+2 & \text{if $r=p$ and $q$ supported on $m+1$} \\
    I_{m+1}^{(V)}(r) & \text{if } r\neq p,q
  \end{cases}\\
  I_{m+2}^{(W)}(r) & = \begin{cases}
    m+2 & \text{if } r=p \\
    I_{m+3}^{(V)}(r) & \text{if } r\neq p
  \end{cases}\\
  I_{m+3}^{(W)}(r) & = \begin{cases}
    m+3 & \text{if } r=p \\
    I_{m+4}^{(V)}(r) & \text{if } r\neq p
  \end{cases}
\end{align*}
Note that $I_{m+2}^{(V)}(r) = I_{m+3}^{(V)}(r)$ for all propagators $r$ in $V$, and that if $j+1\not\in\{m, m+1, m+2, m+3\}$ then $j+2$ and $j+3$ are unsupported in $V$ so in that case $I_{j+2}^{(V)}(r) = I_{j+3}^{(V)}(r) = I_{j+4}^{(V)}(r)$ for $r$ in $V$. Therefore, once again we can see that the $J_r^{(W)}(*)$ are cyclic for all $r$ in $V$.  Assembling the intervals for $p$ we get,
 if $m=j$ then
\[J_p^{(W)}(m) = [m+4,e-1], \  J_p^{(W)}(m+1) = [e,m], \  J_p^{(W)}(m+2) = [m+1,m+2], \  J_p^{(W)}(m+3) = \{m+3\},\]
 if $m=j+1$ then
\[J_p^{(W)}(m) = [m+4,m-1], \ J_p^{(W)}(m+1) = [m,m+1], \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\},\]
and if $m=j+2$ then
\[J_p^{(W)}(m) = [m+4,m], \  J_p^{(W)}(m+1) = \{m+1\}, \  J_p^{(W)}(m+2) = \{m+2\}, \  J_p^{(W)}(m+3) = \{m+3\}.\]
The result now follows by induction.
